---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SAT

<!-- badges: start -->
<!-- badges: end -->

The goal of SAT is to ...

## Installation

You can install the released version of SAT from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("SAT")
```

And the development version from [GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("JianqiaoWang/SAT")
```
## Example

This is a basic example which shows you how to solve a common problem: Independent sequence

```{r example}
library(SAT)
## basic example code
p <- 1*10^5; ## total number of pairs
d1 = 100; d2 = 100; d3 = 1;
X <- c(rep(0,p-(d1 + d2 + d3)),rep(1,d1),rep(2,d2),rep(3,d3));
mu.1 = rep(0, p); mu.2 = rep(0, p);
mu.1[X==1|X==3] = 4; mu.2[X==2|X==3] = 5;
Z1 <- mu.1 + rnorm(p,0,1);
Z2 <- mu.2 + rnorm(p,0,1);
T1 = abs(Z1);T2 = abs(Z2);
P1 = 2* (1 - pnorm( T1)); P2 = 2* (1 - pnorm(T2));
SAT::MinDetect(P1, P2)
```


For the typical genetic applications, we consider the LD between the sequences. It requires the additional information of the external LD matrix.  

```{r, eval = F}
pvalue =  SAT::MinMaxP.geno(sumstat.comb$P.gwas, sumstat.comb$P.gtex, ref.geno = geno, ref.bed = "../geno/GTEx_WGS_838Indiv_Freeze_phased_MAF_0.01_chr1_22_EU",
                            output.dir = output.dir, var.name = sumstat.comb$variant_id, block.thresh = 0.99)

```
